Unveiling the 2022 Iran Protests: Insights from HRANA's Dataset

### 2024-04-03 paper/paper.qmd
Typo fixed

## Beyond Mahsa Amini: Exploring Gender Inequality and Activism in the Context of the 2022 Iran Protests

@@

## The Importance of Accurate and Comprehensive Data in Understanding Civil Unrest

>>>>

## Beyond Mahsa Amini: Exploring Gender Inequality and Activism

@@

## The Importance of Accurate and Comprehensive Data
